Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/data-collection.tex

We take data from \vgenome~\cite{krishna2016visualgenome}, which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vgenome (VG) suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.

@@

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
This yielded $25,596$ images (we discarded $5,497$).
We then did 3 more collection rounds, obtaining a total of 36 images per object.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

>>>>

We take data from \vgenome~(VG, \newcite{krishna2016visualgenome}), which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and have a high number of \vg object instances of different names.\cs{prev. sentence this is still a bit fluffy}
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains.

@@

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vg name.
This yielded $25,596$ images (we discarded $5,497$).
We then did 3 more collection rounds, obtaining a total of 36 images per object.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
